\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{hyperref}

\geometry{
	a4paper,
	margin=20mm
}

\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy}

\usepackage[style=ieee, backend=biber, doi=false, isbn=false, eprint=false, url=false]{biblatex}
\addbibresource{bibliography.bib}
\appto\bibfont{\setlength{\emergencystretch}{.5em}}

\fancyhf{}

\allowdisplaybreaks

\title{
    A Nonoverlapping Three-Grid, Two-Level Schwarz Method on a Single GPU
}
\author{Mieszko Grodzicki}
\date{}

\begin{document}

\maketitle

Relatively little work has been done so far on the efficiency of domain decomposition
methods for PDEs on GPUs. This is partly because their usual coarse-grained
parallelism does not map well to highly multithreaded GPUs. Therefore, methods
capable of massive parallelism are preferable for GPU-based solvers. For elliptic PDEs,
a possible approach, promising a~high level of concurrency, is a Schwarz
method based on three-grid, two-level domain decomposition \cite{Przykry},
whose main ingredient is to solve a~very large number of independent local
subproblems in parallel. The method was designed for a~discontinuous Galerkin
approximation of the diffusion equation with a high-contrast coefficient.

In this paper, we develop an implementation of the method on a single GPU.
To identify the best\nobreakdash-performing configuration, we conduct a series of experiments in which
we compare the additive and hybrid variants of the method, and investigate how
the size of the local problems and the granularity of the coarse grid affect performance.
We also introduce mixed-precision variants; in particular, we show
that using half precision in the local solvers (for a double-precision problem)
yields significant speedup with negligible impact on convergence.

The obtained solver is highly efficient: individual components
achieve $70-90\%$ of the measured peak memory bandwidth of an NVIDIA A100 GPU.
A comparison with the state-of-the-art GPU-based AMG solver AmgX shows that our
implementation delivers competitive solution times, especially
for high-degree 3D problems, where performance of AmgX degrades.
Our results further demonstrate that even on a single A100 with 80GB of memory,
the matrix-based approach is capable of solving even moderately large elliptic problems
-- up to 100M DoFs in 2D and 50M DoFs in 3D -- while readily handling variable
coefficients and nonuniform meshes.

% TODO: format referencji taki jak chca w artykule?
\printbibliography

\end{document}
